I've Got Nothing to Hide: \\ Exploring Privacy in Art, Books, and Film

### 2013-09-26 nothing_to_hide/presentation.tex
update.
Added little brother and art project

\frametitle{\emph{The Neighbors} by Arne Svenson}

@@

>>>>

\frametitle{\emph{The Neighbors} (2013) by Arne Svenson}

@@

\begin{frame}
\frametitle{Face to Facebook}

Stealing 1 million Facebook profiles, filtering them with face-recognition software, and then,
posting them on a custom-made dating website, sorted by their facial
expressions characteristics.

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command
    \begin{itemize}
    \item All ``singles'' were involuntarily added to a fake an
      experimental dating site.
    \item Let's watch the introduction video.
    \item Great example of \emph{secondary usage}

    \column{.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth,height=0.4\textheight,keepaspectratio]{img/fbFaces}
    \caption{Facebook Faces by Joern Roeder and Jonathan Pirnay,
      University of Visual Arts and Design Kassel, Germany, 2011}

    \end{figure}

\begin{frame}
\frametitle{\emph{The Trial} by Franz Kafka}

\begin{itemize}
\item Referred to by the author as an example that ``depicts a
  bureaucracy with insrutable purposes that uses people's information
  to make important decisions about them, yet denies the people the
  ability to participate in how their information is used.''

\item Reading from beginning of \emph{The Trial}.
\item Reading from \emph{Harper's}, September 2013, \emph{Life as a
  Terrorist: Uncovering my FBI File} by William T. Vollmann
\end{itemize}

\begin{block}{I have nothing to hide.}
    But when the government hides information about you, it enables a
    sense of frustration and powerlessness.
  \end{block}

\begin{frame}
\frametitle{\emph{Little Brother} and \emph{Homeland} by Cory
  Doctorow}

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command
    \begin{itemize}
    \item Cory Doctorow: EFF, Boing Boing, several books.
    \item The day after tomorrow setting: terrorist attack San Francisco.
    \item \emph{Little Brother} teaches you how to have a GPG Signing
      party and how to run anonymizing software (like Tails and Tor).
    \item Afterwards by Bruce Schneier, Andrew Huang, Jacob Appelbaum,
      Aaron Schwartz.
    \item \emph{Little Brother} has an \emph{excellent} Bibliography for
      other readings on security.
    \end{itemize}

    \column{.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{img/Little-Brother}

    \end{figure}

\end{frame}
\begin{frame}
